---
title: "Skin Temperature"
description: "Computes the calibrated skin temperature assuming amp run in DC, according to corresponding gain and chosen temperature scale for each respondent"
helpUrl: https://go.imotions.com/Skin_Temperature
dependencies:
  sensor: "Biopac"
params:
  token: "xxxxx"
  studyId: "xxxxx"
  respondentId: "xxxxx"
  selectedSensorName: ""
  flowName: "xxxxx"
  iMotionsVersion: "xxxxx"
  GainSelection:
   label: "Select corresponding gain used"
   value: "1"
   selected: "1"
   input: select
   choices: ["0.5", "1", "2", "5"]
  TemperatureScaleSelection:
   label: "Choose temperature scale"
   value: "Fahrenheit (deg F)"
   selected: "Fahrenheit (deg F)"
   input: select
   choices: ["Fahrenheit (deg F)", "Celsius (deg C)"]
output:
  html_document:
    df_print: kable
    code_folding: hide
    code_download: true
---

```{r global_options, include=FALSE}
library(imotionsApi)
library(data.table)
library(dplyr)
library(kableExtra)
library(knitr)

start_time <- Sys.time()
```

```{r Parameters, purl = TRUE}
# Retrieves parameters
gain <- as.numeric(params$GainSelection)
temp_scale <- params$TemperatureScaleSelection
```

```{r Get skin temperature sensor, purl = TRUE}
#' Retrieving skin temperature data
#'
#' @param study An imStudy object as returned from \code{\link{imotionsApi::imStudy}}.
#' @param respondent An imRespondent object as returned from \code{\link{imotionsApi::getRespondents}}.
#' @param selectedSensorName selectedSensorName from software dropdown - cloud value is empty and we use autodetection
#'
#' @details Supports Biopac
#'
#' @return A data.table containing the requested skin temperature data
getSkintempData <- function(study, respondent, selectedSensorName) {
    # Now it retrieves all sensors for a respondent of interest
    rSensors <- getSensors(study, respondent)

    rSensors <- rSensors[!sensor == "R Analysis" & eventSourceType == "Sensor", ]

    # in case of empty selectedSensorName (cloud data), the function will autodetect it
    sensorSensor <- unlist(strsplit(selectedSensorName, "||", fixed = T))[1]
    sensorName <- unlist(strsplit(selectedSensorName, "||", fixed = T))[2]
    sensorInstance <<- unlist(strsplit(selectedSensorName, "||", fixed = T))[3]

    if ((!is.na(sensorSensor) & sensorSensor == "Biopac") || (is.na(sensorSensor) && "Biopac" %in% rSensors$sensor)) {
        message("Biopac Sensor identified.")
        tempSensorIdx <- grepl("SKT100C", rSensors$instance) & grepl("Biopac", rSensors$sensor)
        instanceIdx <- sensorInstance == rSensors$instance

        # if the instance name match a skin temperature data we use this one, else we select the first device found
        if (sum(tempSensorIdx & instanceIdx, na.rm = T) == 1) {
            tempSensorIdx <- tempSensorIdx & instanceIdx
        }

        if (sum(tempSensorIdx) == 0) {
            message("Skin temperature sensor not found.")
            return(NULL)
        }

        if (sum(tempSensorIdx) > 1) {
            infoMessage("More than one Biopac device is present. Using the first one.")
        }

        ## Retrieves the names of the signals as they can vary...
        sensor <- rSensors[tempSensorIdx, ][1, ]
        signalNames <- rSensors[tempSensorIdx, ]$signals[[1]]
        signalName <- signalNames[grepl("Raw", signalNames)]

        if (!signalName %in% signalNames) {
            message("The skin temperature signal was not found.")
            return(NULL)
        }

        # Retrieves data for respondent, containing the Timestamp and Signal column
        Temp_Raw <- getSensorData(study, sensor, signalName)

        estimated_sample_rate <- 1000 / median(diff(Temp_Raw$Timestamp))
        message(paste("Sample rate:", estimated_sample_rate, "Hz"))

        attr(Temp_Raw, "sensor") <- sensorInstance
        attr(Temp_Raw, "sensor and channel type") <- "Biopac"
    }

    # Renames the Signal column to Volt
    names(Temp_Raw)[2] <- "Volt"
    return(Temp_Raw)
}
```

```{r set, purl = FALSE}
studyId <- params$studyId
respondentId <- params$respondentId
selectedSensorName <- params$selectedSensorName

### Connect to iMotions and retrieve informations
connection <- imConnection(params$token)
study <- imStudy(connection, studyId)
respondent <- getRespondent(study, respondentId)

studyName <- study$name
respondentName <- respondent$name
```

```{r Raw data to temperature, purl = FALSE}
Temp_signal <- getSkintempData(study, respondent, selectedSensorName)

# Converting to Fahrenheit and adjusting with corresponding gain
Temp_signal$Volt <- (Temp_signal$Volt * gain) + 90

# Converts to Celsius if it is chosen, otherwise proceeded with Fahrenheit
# Columns are furthermore renamed according to chosen temperature scale
if (temp_scale == "Celsius (deg C)") {
    colname <- "Skin Temperature (deg C)"
    Temp_signal$Volt <- (Temp_signal$Volt - 30) / 2
} else {
    colname <- "Skin Temperature (deg F)"
}

setnames(Temp_signal, "Volt", colname)
```


```{r Upload, purl = FALSE}
#Uploading the converted signals
ul_temp_signal <- uploadSensorData(params, study, Temp_signal, respondent, sensorName = "Calibrated Skin Temperature",
                                   scriptName = "Skin-Temperature")

end_time <- Sys.time()
time_taken <- end_time - start_time
```

#### Study: ``r studyName``
#### Respondent: ``r respondentName``

--- 
This R notebook has performed the following steps:

* Retrieval of the raw signal (Volt, V) from the sensor.

* Generates the calibrated skin temperature in `r temp_scale` based on raw signal amplified by a gain of `r gain`. 

*Computation started at `r format(start_time, usetz = TRUE)` / Notebook execution time: `r format(time_taken)`*

### References

```{r license, echo = FALSE}
# The contents of this notebook are licensed under the MIT license:
# Copyright (c) 2018 iMotions
#
# Permission is hereby granted, free of charge, to any person obtaining a copy
# of this software and associated documentation files (the "Software"), to deal
# in the Software without restriction, including without limitation the rights
# to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
# copies of the Software, and to permit persons to whom the Software is
# furnished to do so, subject to the following conditions:
#
# The above copyright notice and this permission notice shall be included in all
# copies or substantial portions of the Software.
#
# THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
# IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
# FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
# AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
# LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
# OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
# SOFTWARE.
```



